Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-21 paper/paper.tex
Change figure captions of main

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig1.pdf}
  \caption{\textbf{Experimental setup and nanopore characterization}.
    \textbf{a}. 3D schematic diagram showing the experimental
    setup. Inset: photograph of the PG-PCTE membrane supported by
    Kapton and copper tapes, scale bar: 1 cm. \textbf{b}. 3D schematic
    of the nanoscale cross-sectional structure of the PG-PCTE
    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showing
    excellent coverage of graphene over the PCTE substrate, scale bar:
    20 $\mathrm{\mu}$m.  Upper right inset: high-resolution SEM image
    of individual nanopores on PG fabricated by the patterning
    technique, scale bar: 500 nm. Bottom right inset: histogram of the
    pore diameter distribution revealed by the SEM
    image. \textbf{d}. Schematic of the nanoscale ionic transport
    through a gated graphene nanopore.}
  \label{fig:1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig2.pdf}
  \caption{\textbf{The experimental evidence of salt rejection.}
    \textbf{a}. Measured conductivity of LCR as a function of
    time. The slope of conductivity-time curve when $V_{\mathrm{G}}>0$
    is added, is smaller than that without gating. \textbf{b}. Molar
    diffusive flux through bare PCTE (blue bars: experimental; red
    bars: theoretical values) and PG+PCTE (green bars) membranes for
    different salts. \textbf{c}. Experimentally measured salt
    rejection factor $\xi$ as a function of $V_{\mathrm{G}}$ for 0.1
    mM KCl solution in HCR, showing an asymmetric response, with a
    higher degree of salt rejection for
    $V_{\mathrm{G}}>0$. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
    of KCL concentration, fitted by a power law relation, suggesting
    the effect of Debye length on the observed salt rejection. }
  \label{fig:2} 
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig3.pdf}
  \caption{\textbf{Interplay between graphene quantum capacitance and
      EDL.} \textbf{a}. Schematic diagram of the electrostatic
    potential at the graphene-electrolyte interface considering the
    quantum capacitance of graphene. The interfacial potential of the
    electrolyte solution, $\psi_{0}$, is smaller than the bias
    $V_{\mathrm{G}}$ applied, as a result of the change of graphene’s
    Fermi level $\Delta \phi_{\mathrm{G}}$ and the potential drop in
    the Stern layer $\Delta \psi$. \textbf{b}. Calculated surface
    charge $\sigma_{\mathrm{G}}$ and surface potential
    $\psi_{\mathrm{G}}$ of graphene as a function of $V_{\mathrm{G}}$
    in a 1 mM KCl solution. }
  \label{fig:3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig4.pdf}
  \caption{\textbf{Self-consistent theoretical
      calculations}. \textbf{a}. Calculated cross-sectional contour
    plot of electrostatic potential $\psi$ near the center of the
    graphene nanopore at $V_{\mathrm{G}}$ = 0.75 V. \textbf{b}. The
    corresponding electrochemical potential change for cation
    $\Delta \mu_{+}$ (left) and anion $\Delta \mu_{-}$ (right). The
    reference of electrochemical potential is set in the HCR far from
    the graphene layer. The diffusive pathways for both ions are
    indicated by arrows. \textbf{c}. Calculated z-component of
    diffusive fluxes $\boldsymbol{J}_{z}$ for cation (left) and anion
    (right) through the pore as functions of the relative position
    inside the pore, considering different levels of $V_{\mathrm{G}}$
    applied. \textbf{d}. Calculated z-components of cation, anion, and
    total fluxes through the graphene nanopore as functions of
    $V_{\mathrm{G}}$, showing salt rejection for all fluxes.}
  \label{fig:4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{The Debye length effect}. \textbf{a}. Contour plot
    of the surface potential of graphene $\psi_{\mathrm{G}}$ as a
    function of $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
    $V_{\mathrm{G}}$. When the Debye length reduces, a higher
    $V_{\mathrm{G}}$ is required to maintain the same surface
    $\psi_{\mathrm{G}}$ level. \textbf{b}. 2D contour plot of
    theoretically predicted $\xi$ as a function of
    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
    $V_{\mathrm{G}}$. Clearly, a higher degree of salt rejection can
    be achieved by having a higher $V_{\mathrm{G}}$ and
    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ ratio.}
  \label{fig:5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig6.pdf}
  \caption{\textbf{Comparison between experiments and simulations
      considering different salt species}. \textbf{a}. Experimentally
    measured $\xi$ as a function of $V_{\mathrm{G}}$ for various salts
    at 0.1 mM. The error bar indicates the standard
    error. \textbf{b}. Simulated $\xi-V_{\mathrm{G}}$ relations for
    the salt species considered here. \textbf{c}. Comparison between
    the experimental and calculated $\xi_{\mathrm{max}}$ values for
    different salt species, decreasing with the salt
    valence. \textbf{d}. $\xi_{\mathrm{max}}$ as a function of
    $\lambda_{\mathrm{D}}$ for the experimental (circle) and model
    (diamond) values, with a linear correlation.}
  \label{fig:6}
\end{figure}

>>>>

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\DeclareCaptionLabelSeparator{bar}{  \textbar\quad}
\usepackage[labelsep=bar, labelfont=bf]{caption}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

% \makeatletter
% \renewcommand*{\fnum@figure}{{\normalfont\bfseries \figurename~\thefigure}}
% \renewcommand*{\@caption@fignum@sep}{\textbf{ \textbar }}
% \makeatother

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig1.pdf}
  \caption{\textbf{Experimental setup and nanopore characterization}.
    \textbf{a}. 3D schematic diagram showing the experimental
    setup. Inset: photograph of the PG-PCTE membrane supported by
    Kapton and copper tapes. (Scale bar: 1 cm.) \textbf{b}. 3D schematic
    of the nanoscale cross-sectional structure of the PG-PCTE
    membrane. \textbf{c}. SEM image of the PG-PCTE membrane, showingan
    excellent coverage of graphene over the PCTE substrate, scale bar:
    20 $\mathrm{\mu}$m.  Upper right inset: high-resolution SEM image
    of individual nanopores on PG fabricated by the patterning
    technique. (Scale bar: 500 nm.) Bottom right inset: histogram of the
    pore diameter distribution revealed by the SEM
    image. \textbf{d}. Schematic of the nanoscale ionic transport
    through a gated graphene nanopore.}
  \label{fig:1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig2.pdf}
  \caption{\textbf{The experimental evidence of salt rejection.}
    \textbf{a}.An example of measured conductivity in LCR as a
    function of time. The slope of conductivity-time curve when
    $V_{\mathrm{G}}>0$ is interpolated, is smaller than that without
    gating. \textbf{b}. Molar diffusive flux through bare PCTE (blue
    bars: experimental; red bars: model values) and PG+PCTE (green
    bars) membranes for different salts. \textbf{c}. Experimentally
    measured salt rejection factor $\xi$ as a function of
    $V_{\mathrm{G}}$ for 0.1 mM KCl solution in HCR, showing an
    asymmetric response, with a higher degree of salt rejection for
    $V_{\mathrm{G}}>0$. \textbf{d}. $\xi_{\mathrm{max}}$ as a function
    of KCl concentration, fitted by a power law relation, suggesting
    the effect of Debye length on the observed salt rejection, since
    $\lambda_{\mathrm{D}} \propto c_{0}^{-\frac{1}{2}}$.}
  \label{fig:2} 
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig3.pdf}
  \caption{\textbf{Interplay between graphene quantum capacitance and
      EDL.} \textbf{a}. Schematic diagram of the electric
    potential at the graphene-electrolyte interface considering the
    quantum capacitance of graphene. The interfacial potential of the
    electrolyte solution, $\psi_{0}$, is smaller than the bias
    $V_{\mathrm{G}}$ applied, as a result of the change of graphene’s
    Fermi level $\Delta \phi_{\mathrm{G}}$ and the potential drop in
    the Stern layer $\Delta \psi$. \textbf{b}. Calculated surface
    charge $\sigma_{\mathrm{G}}$ and surface potential
    $\psi_{\mathrm{G}}$ of graphene as a function of $V_{\mathrm{G}}$
    in a 1 mM KCl solution. }
  \label{fig:3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig4.pdf}
  \caption{\textbf{Calculations using the proposed self-consistent
      theory}. \textbf{a}. Calculated cross-sectional contour plot of
    electric potential $\psi$ near the center of the graphene
    nanopore at $V_{\mathrm{G}}$ = 0.75 V. \textbf{b}. The
    corresponding electrochemical potential change for cation
    $\Delta \mu_{+}$ (left) and anion $\Delta \mu_{-}$ (right). The
    reference of electrochemical potential is set in the HCR far from
    the graphene layer. The diffusive pathways for both ions are
    indicated by the arrows. \textbf{c}. Calculated z-component of
    diffusive fluxes $\boldsymbol{J}_{z}$ for cation (left) and anion
    (right) through the pore as functions of the relative position
    inside the pore, considering different levels of $V_{\mathrm{G}}$
    applied. \textbf{d}. Calculated z-components of cation, anion, and
    total fluxes through the graphene nanopore as functions of
    $V_{\mathrm{G}}$, showing salt rejection for all fluxes.}
  \label{fig:4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{The Debye length effect on the degree of salt
      rejection}. \textbf{a}. Calculated contour plot of the surface
    potential of graphene $\psi_{\mathrm{G}}$ as a function of
    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$. When
    the Debye length reduces, a higher $V_{\mathrm{G}}$ is required to
    maintain the same surface $\psi_{\mathrm{G}}$
    level. \textbf{b}. Calculated 2D contour plot of theoretically
    predicted $\xi$ as a function of
    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and
    $V_{\mathrm{G}}$. Clearly, a higher degree of salt rejection can
    be achieved by having a higher $V_{\mathrm{G}}$ and
    $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$}
  \label{fig:5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig6.pdf}
  \caption{\textbf{Comparison between experimental and theoretical
      salt rejection considering different salt
      species}. \textbf{a}. Experimentally measured $\xi$ as a
    function of $V_{\mathrm{G}}$ for various salts at 0.1 mM. The
    error bar represents the standard error. \textbf{b}. Theoretically
    calculated $\xi-V_{\mathrm{G}}$ relations for the salt species
    considered here. \textbf{c}. Comparison between the experimental
    and calculated $\xi_{\mathrm{max}}$ values for different salt
    species, decreasing with the salt
    valence. \textbf{d}. $\xi_{\mathrm{max}}$ as a function of
    $\lambda_{\mathrm{D}}$ for the experimental (circle) and model
    (diamonds) values, showing a linear correlation.}
  \label{fig:6}
\end{figure}
